Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-18 manuscript/manuscript.Rmd
more results

authors: 
- name: Felipe Montealegre-Mora
  address: Department of Environmental Science, Policy, and Management, University of California, Berkeley
- name: Marcus Laperolerie
  address: Department of Environmental Science, Policy, and Management, University of California, Berkeley
- name: Melissa Chapman
  address: Department of Environmental Science, Policy, and Management, University of California, Berkeley
- name: Carl Boettiger
  address: Department of Environmental Science, Policy, and Management, University of California, Berkeley
  email: cboettig@berkele.edu

@@

We trained a DRL agent to obtain a candidate policy
\begin{align*}
  \pi: (X_t,Y_t,Z_t) \mapsto h_t
\end{align*}
for eq. \eqref{eq:3d model}.
The agent could fully and precisely observe the state of the system at each time step and decide on its harvest based on this information.

>>>>

authors: 
- name: Felipe Montealegre-Mora
  address: Department of Environmental Science, Policy, and Management, University of California, Berkeley
- name: Marcus Laperolerie
  address: Department of Environmental Science, Policy, and Management, University of California, Berkeley
- name: Melissa Chapman
  address: Department of Environmental Science, Policy, and Management, University of California, Berkeley
- name: Abigail G. Keller
  address: Department of Environmental Science, Policy, and Management, University of California, Berkeley
- name: Carl Boettiger
  address: Department of Environmental Science, Policy, and Management, University of California, Berkeley
  email: cboettig@berkele.edu

@@

We trained a DRL agent to obtain a candidate policy
\begin{align*}
  \pi: (X_t,Y_t,Z_t) \mapsto h_t
\end{align*}
for eq. \eqref{eq:3d model}.
The agent could fully and precisely observe the state of the system at each time step and decide on its harvest based on this information. 
The agent was trained using the PPO algorithm, using a neural network with two hidden layers of 64 neurons to express $\pi$.
Details of the training process may be found in App. \ref{app:tbd}.
Our code is available at TBD.

We compare the performance of this agent to the performance of MSY and of an 80% TAC.

Our results suggest that DRL can find solutions that are more sustainable *and* more profitable than both MSY and TAC.
Indeed, DRL finds solutions in which, for certain periods of time, no harvest is performed on the system.
These periods effectively allow the system to, in a sense, ‘‘reset’’ itself.
They lead to a distinctive oscillating behavior of the system state over time, with periods of relative depletion followed by periods of growth. 
Figure \ref{fig:tbd} exemplifies this point by comparing the harvest effort and state times series obtained from these policies.

It is well known that following MSY policies can lead to over-fishing.
Our results reproduce this behavior and, furthermore, warn that using a TAC policy instead might not be enough to gain sustainability.
Figure TBD-A shows the mean episode length for
